\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-20 latex/UMEM_CoSim.tex
A few more comments added

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less

@@

\subsection{CitySim co-simulation results}\noteCM{Jerome -- I really need some help interpreting this...}

When focusing on solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.

>>>>

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less prounced that the HPI case study. \noteCM{I'm planning to elaborate on these sections but am struggling to interpret the results other than just "co-sim and solo are difference" -- what do you guys think?}

@@

\subsection{CitySim co-simulation results}

When focusing on solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}. \noteCM{Jerome -- I need some help interpreting these results -- you mentioned that there is an expected delta between citysim and energyplus in previous studies. Can you help elaborate on that?}
